Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-10 doc/peakcharacterization_manuscript.Rmd
oops

```{r normalization_data, eval = FALSE}
# figure showing peak intensity correlation with M/Z, intensity varying with M/Z
tar_load(correlate_scan_height_plot_correlate_scan_height_data)
correlate_scan_height_plot_correlate_scan_height_data
```

*caption*: **A**: An example of a peak whose height across scans is correlated with scan number.
**B**: The peak differences to the same peaks in a reference scan are plotted against peak height.
Black: Peaks with a height < 0.7 of the maximum. 
Red: Peaks with a height >= 0.7 of the maximum.

>>>>

```{r increment_intensity_scan}
figure_count$increment("intensity_scan")
```

```{r intensity_scan, dn_id = figure_count}
# figure showing peak intensity correlation with M/Z, intensity varying with M/Z
tar_load(intensity_scan_cor_plot)
intensity_scan_cor_plot
```

`r figure_count$label_text("intensity_scan")`. 
**A**: An example of a peak whose height across scans is correlated with scan number.
**B**: The peak differences to the same peaks in a reference scan are plotted against peak height.
Black: Peaks with a height < 0.7 of the maximum. 
Red: Peaks with a height >= 0.7 of the maximum.
